---
title: "lesson5 (multiple variables)"
author: "wwj"
date: "2017年10月31日"
output: html_document
editor_options: 
  chunk_output_type: console
---
## Third Qualitative Variable
```{r}
library(dplyr)
library(ggplot2)
getwd()
setwd("C:/Users/wj/desktop/R")
pf <- read.csv("facebook.tsv", sep = "\t")

pf.fc_by_age_gender <- pf %>%
  group_by(age, gender) %>%
  filter(!is.na(gender)) %>%
  summarise(mean_friend_count = mean(friend_count),
            median_friend_count = median(friend_count),
            n = n()) %>%
  arrange(age)
head(pf.fc_by_age_gender)
```

## Plotting Conditional Summaries
```{r}
ggplot(aes(x = age, y = median_friend_count),
       data = pf.fc_by_age_gender) +
  geom_line(aes(color = gender))
```

## Reshaping Data
```{r}
install.packages('reshape2')
library(reshape2)

pf.fc_by_age_gender.wide <- dcast(pf.fc_by_age_gender,
                                  age ~ gender,
                                  value.var = 'median_friend_count')
head(pf.fc_by_age_gender.wide)

```

## Ratio Plot Solution
```{r}
ggplot(aes(x = age, y = female/male),
       data = pf.fc_by_age_gender.wide) +
  geom_line() +
  geom_hline(yintercept = 1, color = "blue", linetype = 2, alpha = 0.5)
```

## Third Quantitative Variable
```{r}
pf$year_joined <- floor(2014 -pf$tenure/365)

```

## Cut a Variable
```{r}
table(pf$year_joined)

#(2004-2009]
#(2009-2011]
#(2011-2012]
#(2012-2014]

pf$year_joined.bucket <- cut(pf$year_joined,
                             c(2004, 2009, 2011, 2012, 2014))
```

## Plotting it All Together Solution
```{r}
ggplot(aes(x = age, y = friend_count),
       data = subset(pf, !is.na(year_joined.bucket))) +
  geom_line(aes(color = year_joined.bucket), 
            stat = "summary", 
            fun.y = median )
```

## Plot the Grand Mean Solution
```{r}
ggplot(aes(x = age, y = friend_count),
       data = subset(pf, !is.na(year_joined.bucket))) +
  geom_line(aes(color = year_joined.bucket), 
            stat = "summary", 
            fun.y = mean) +
  geom_line(stat = "summary",
            fun.y = mean,
            linetype = 2)
```

## Friending Rate
```{r}
with (subset(pf, tenure >=1), summary(friend_count / tenure))
```

## Friendships Initiated Solution
```{r}
ggplot(aes(x = tenure, y = friendships_initiated / tenure),
       data = subset(pf, tenure >= 1)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)
```

## Bias-Variance Tradeoff Revisited
```{r}
ggplot(aes(x = tenure, y = friendships_initiated / tenure),
       data = subset(pf, tenure >= 1)) +
  geom_smooth(aes(color = year_joined.bucket))
```


# Yogurt

## Histograms Revisited
```{r}
yo <- read.csv('yogurt.csv')
str(yo)

# Change the id from an int to a factor
yo$id <- factor(yo$id)
str(yo)
```

## Histograms Revisited Solution
```{r}
qplot(x = price, data = yo, color = I("black"), fill = I("blue"))
```

## Number of Purchases
```{r}
yo <- transform(yo, all.purchases = strawberry + blueberry + pina.colada + plain + mixed.berry)

summary(yo$all.purchases)

# alternate verbose form
yo$all.purchases <- yo$strawberry +yo$blueberry + yo$pina.colada + yo$plain + yo$mixed.berry
```

## Prices over Time
```{r}
qplot(x = all.purchases, data = yo, binwidth = 1,
      fill = I("#099DD9"))
```

## Prices over Time Solution
```{r}
str(yo)

ggplot(aes(x = time, y = price), data = yo) +
  geom_jitter(alpha = 1/4, shape = 21, fill = I("#F79420"))
```

## Looking at Samples of Households
```{r}
# Set the seed for reproducible results
set.seed(4130)
sample.ids <- sample(levels(yo$id), 16)

ggplot(aes(x = time, y = price),
       data = subset(yo, id %in% sample.ids)) +
  facet_wrap(~ id) +
  geom_line() +
  geom_point(aes(size = all.purchases), pch = 1)
```

## Scatterplot Matrices
```{r}
install.packages("GGally")
library(GGally)
theme_set(theme_minimal(20))

# set the seed for reproducible results
set.seed(1836)
pf_subset <- pf[, c(2:15)]
names(pf_subset)
ggpairs(pf_subset[sample.int(nrow(pf_subset), 1000), ])
```

