---
title: "lesson4(two variables)"
author: "wwj"
date: "2017å¹?10æœ?30æ—?"
output: html_document
editor_options: 
  chunk_output_type: console
---
lesson4
===============================================
## Scatter Plots
```{r}
getwd()
setwd("C:/Users/wj/desktop/R")
library(ggplot2)
pf <- read.csv("facebook.tsv", sep = "\t")

qplot(x = age, y = friend_count, data = pf)
qplot(age, friend_count, data = pf)
```

## ggplot Syntax
```{r}
qplot(x = age, y = friend_count, data = pf)

ggplot(aes(x = age, y = friend_count), data = pf)+
  geom_point() + xlim(13, 90)

summary(pf$age)
```


## Overplotting
```{r}
ggplot(aes(x = age, y = friend_count), data = pf)+
  geom_jitter(alpha = 1/20) +
  xlim(13, 90)
```

## coord_trans()
```{r}
ggplot(aes(x = age, y = friend_count),data = pf) +
  geom_point(alpha = 1/20) +
  xlim(13, 90) +
  coord_trans(y = "sqrt")
```

## Alpha and Jitter
Explore the relationship between friends initiated vs age.
```{r}
names(pf)
ggplot(aes(x = age, y = friendships_initiated), data = pf) +
  geom_point(alpha = 1/10, position = position_jitter(h = 0)) +
  xlim(13, 90) +
  coord_trans(y = "sqrt")
```

## Conditional Means
```{r}
library('dplyr')

filter()
group_by()
mutate()
arrange()

age_groups <- group_by(pf, age)
pf.fc_by_age <- summarise(age_groups,
                        friend_count_mean = mean(friend_count),
                        friend_count_median = median(friend_count),
                        n = n())
pf.fc_by_age <- arrange(pf.fc_by_age, age)
head(pf.fc_by_age)
```

## Conditional Means Alternate Code
```{r}
pf.fc_by_age <- pf %>%
  group_by(age)%>%
  summarise(friend_count_mean = mean(friend_count),
            friend_count_median = median(friend_count),
            n = n()) %>%
  arrange(age)

head(pf.fc_by_age)
```

## Create line plot
```{r}
ggplot(aes(x = age, y = friend_count_mean),data = pf.fc_by_age) +
  geom_line()
```

## Overlaying Summaries with Raw Data
```{r}
ggplot(aes(x = age, y = friend_count), data = pf) +
  geom_point(alpha = 0.05,
             position = position_jitter(h = 0),
             color = "orange") +
  coord_cartesian(xlim = c(13, 90), ylim = c(0, 1000)) +
  geom_line(stat = "summary", fun.y = mean) +
  geom_line(stat = "summary", fun.y = quantile, 
            fun.args = list(probs = 0.1),
            linetype = 2, color = "blue") +
  geom_line(stat = "summary", fun.y = quantile,
            fun.args = list(probs = 0.5),
            color = "red") +
  geom_line(stat = "summary", fun.y = quantile,
            fun.args = list(probs = 0.9),
            linetype = 2, color = "green")
```

## Correlation
```{r}
cor(pf$age, pf$friend_count)

cor.test(pf$age, pf$friend_count, method = "pearson")

with(pf, cor.test(age, friend_count, method = "pearson"))
```

## Correlation on Subsets Solution
```{r}
with(subset(pf, age <= 70), cor.test(age, friend_count, method = "pearson"))
```

## Create Scatter plot with www_likes_received vs likes_received
```{r}
ggplot(aes(x = www_likes_received, y = likes_received), data = pf) +
  geom_point() +
  coord_cartesian(xlim = c(0, 65000), ylim = c(0, 180000))
```

## Strong Correlations
```{r}
ggplot(aes(x = www_likes_received, y = likes_received), data = pf) +
  geom_point() +
  xlim(0, quantile(pf$www_likes_received, 0.95)) +
  ylim(0, quantile(pf$likes_received, 0.95)) +
  geom_smooth(method = "lm", color = "red")
cor.test(pf$www_likes_received, pf$likes_received, method = "pearson")
```

## More Caution with Correlation
```{r}
install.packages('alr3')
install.packages('car')
install.packages('minqa')
library(alr3)
data(Mitchell)
names(Mitchell)
```

```{r}
library(ggplot2)
ggplot(aes(x = Month, y = Temp), data = Mitchell) +
  geom_point() +
  geom_smooth(method = "lm",color = "red")
cor.test(Mitchell$Month, Mitchell$Temp, mothod = "pearson")
```

## Making Sence of Data
```{r}
ggplot(aes(x = Month, y = Temp), data = Mitchell) +
  geom_point() +
  scale_x_continuous(limits = c(0, 203), breaks = seq(0, 203, 12))
```

## Create a 'age_with_months' variable
```{r}
pf$age_with_months <- pf$age + (1 - pf$dob_month/12)
pf.fc_by_age_months <- pf %>%
  group_by(age_with_months) %>%
  summarise(friend_count_mean = mean(friend_count),
            friend_count_median = median(friend_count),
            n = n()) %>%
  arrange(age_with_months)
head(pf.fc_by_age_months)
```

## Create a line plot showing friend_count_mean vs age_with_months
```{r}
ggplot(aes(x = age_with_months, y = friend_count_mean), 
       data = subset(pf.fc_by_age_months, age_with_months < 71)) +
  geom_line()
```

